\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-09 arch.tex
updates

\section{Planning and execution in the \texttt{T-REX} architecture}
\label{sec:arch}

\subsection{The \rx architecture}
\label{sec:arch:trex}

@@

A prime motivation behind the \rx architecture was to design a
controller which could bring automated planning closer to low-level
control of the vehicle while maintaining its reactivity. Traditionally
planning has been deemed computationally expensive with planner
performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for it. In such a situation, the agent may thrash
if the internal state of the plan gets out of synch with the actual
state of the world. As a result the planning problem managed {\em in
  situ} remains fairly detached from low-level control. Most
adaptations at the lower-level reactive layers in contrast are managed
by specialized components (for example GeNoM \comment{} and CLARATy
\comment{}) that rely on different representations for modeling local
control behavior or worse do not have any explicit formal agent
behavior model. The consequent different techniques for specifying
each layer in the architecture results in duplication of effort and a
diffusion of knowledge leading to significant design and integration
issues \cite{ds1report}.  \texttt{IDEA} mitigated most of these issues
by tightly integrating planning and execution in a single
representational and computational framework with a unified
declarative model. Our approach with \texttt{T-REX} builds on this
design methodology albeit in a substantially systematic manner

@@

\rx provides a formal framework described which details partitioning
in \cite{py10} and \cite{rajan12} and is not the focus of this
chapter. Coupled interaction between planning and the world on the
other hand, has a significant implication on how planning can be
integrated in such frameworks; here we show using the \eu planner can
be coupled to our framework. First we link concepts in \eu planning
with the \rx framework.

@@

@@

Consider for example the \rx agent instance we use on our AUV as shown
in Fig. \ref{fig:agent}. In this instance all the reactors (symbolized
by colored boxes) do not have an explicit connection from one to
another but instead rely on a publish/subscribe model on shared state
variables. For instance the \textsf{Pilot} reactor needs the {\em
  externally} managed state information from \textsf{Sensor\_Data} and
\textsf{Nav\_cmd} state variables in order to maintain the internal
state variables \textsf{Waypoint} and \textsf{Nav\_policy}. This
relation applies in two ways:

@@

\item In order to identify its current {\em internal} state values
  this reactor needs to know the current {\em external} state
  information it relies on. In this case the current \textsf{Waypoint}
  the vehicle is heading to can be extracted for example from the
  current \textsf{Nav\_cmd} executed.

\item The future objectives a reactor has on its future \textsf{Internal}
  state will probably imply sub-objectives to be reported to the
  owner of its {\em external} depending on their current values. Again
  if this reactor wants to go ato a specific \textsf{Waypoint} --
  depending on its current position provided by \textsf{Sensor\_Data}
  it can identify a sequence of \textsf{Nav\_cmd} that should
  eventually help him reach this location.

@@

\begin{figure}[!htb]
 \centering
 \includegraphics[scale=0.45]{figs/AUV-agent.pdf}
 \caption{\small A \texttt{T-REX} agent is composed of multiple
   reactors or control loops (rounded boxes) which are connected
   through state variables provided by one reactor ({\color{blue}blue}
   solid line) with multiple possible clients ({\color{green}green}
   dashed lines)}
  \label{fig:agent}
\end{figure}

Overall the \rx architecture helps to abstract to the reactor
interaction to only state variables. Each reactor is practically
ignoring where its {\em external} state information is managed as long
as this information is available and properly maintained so they can
properly manage their own {\em internal} state information which in
turn may be used by other reactors. Such formalism also constrain
reactors interaction to state information exchanges which are two
folds:

@@

\item {\em Observation on the current state values}: This information
  propagates up in the reactor graph at the synchronization phase 
  and occur at the beginning of every time steps (called
  ticks). During this phase the agent provides to each reactor 
  updates on their {\em external} state variables for this tick and
  ask them to compute their {\em internal} state variables values for
  this same tick. By doing so we propagate a consistent view of that
  state of the world throughout all the reactors as time advance.

>>>>

\section{Planning and execution in the \rx architecture}
\label{sec:arch}

@@

\subsection{Introductory concepts}
\label{sec:arch:intro}

A prime motivation behind the \rx architecture was to design a
controller which could bring automated planning closer to low-level
control of the vehicle while maintaining its reactivity. Traditionally
planning has been deemed computationally expensive with planner
performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for it. In such a situation, the agent may thrash
if the internal state of the plan gets out of synch with the actual
state of the world. As a result the planning problem managed {\em in
  situ} remains fairly detached from low-level control. Most
adaptations at the lower-level reactive layers in contrast are managed
by specialized components (for example GeNoM \comment{} and CLARATy
\comment{}) that rely on different representations for modeling local
control behavior or worse do not have any explicit formal agent
behavior model. The consequent different techniques for specifying
each layer in the architecture results in duplication of effort and a
diffusion of knowledge leading to significant design and integration
issues \cite{DS1report}.  \texttt{IDEA} mitigated most of these issues
by tightly integrating planning and execution in a single
representational and computational framework with a unified
declarative model. Our approach with \texttt{T-REX} builds on this
design methodology albeit in a substantially systematic manner

@@

\rx provides a formal framework described which details partitioning
in \cite{py10} and \cite{rajan12} and is not the focus of this
chapter. Coupled interaction between planning and the world on the
other hand, has a significant implication on how planning can be
integrated in such frameworks; here we show using the \eu planner can
be coupled to our framework. First we link concepts in \eu planning
with the \rx framework. Note that in the following treatise, we call
the formal semantic framework of \rx as the 'agent'. Reactors
constitute an entity within this agent and are standalone blocks of
inference.

@@

\subsection{Architectural concepts in \rx}
\label{sec:arch:trex}

@@

Consider for example the \rx agent instance we use on our AUV as shown
in Fig. \ref{fig:agent}. In this instance all the reactors (symbolized
by colored boxes) do not have an explicit connection from one to
another but instead rely on a publish/subscribe model on shared state
variables. For instance the \textsf{Pilot} reactor needs the {\em
  externally} managed state information from \textsf{Sensor\_Data} and
\textsf{Nav\_cmd} state variables in order to maintain the
\emph{internal} state variables \textsf{Waypoint} and
\textsf{Nav\_policy}. This relation applies in two ways:

@@

\item In order to identify its current {\em internal} state values the
  \textsf{Pilot} \comment{double check this mod} needs to know the
  current {\em external} state information it relies on. In this case
  the current \textsf{Waypoint} the vehicle is heading to can be
  extracted for example from the current \textsf{Nav\_cmd} executed.

\item The future objectives a reactor has on \textsf{Internal} state
  will likely imply sub-objectives to be reported to the owner of its
  {\em external} state variables depending on their current
  values. Should the \textsf{Pilot} want to visit a specific
  \textsf{Waypoint} -- given its current position as provided by
  \textsf{Sensor\_Data}, it can identify a sequence of
  \textsf{Nav\_cmd} states that should eventually help it reach this
  location. \comment{this explanation could do with a figure which I
    believe we have used previously}

@@

\begin{figure}[!htb]
 \centering
 \includegraphics[scale=0.45]{figs/AUV-agent.pdf}
 \caption{\small A \rx agent is composed of multiple reactors or
   control loops (rounded boxes) which are connected through state
   variables provided by one reactor ({\color{blue}blue} solid line)
   with multiple possible clients ({\color{green}green} dashed lines)}
  \label{fig:agent}
\end{figure}

Given the above example, the \rx architecture therefore helps abstract
reactor interaction by containing them to state variables. Each
reactor is therefore agnostic where its {\em external} state
information is managed as long as this information is available and
properly maintained for managing {\em internal} state
information. This {\em internal} state in turn may be used by other
reactors. Such a formalism also constrains reactor interaction to
state information exchange which comes in two forms:

@@

\item {\em Observation on the current state values}: This information
  propagates up in the reactor dependency graph at the synchronization
  phase and occurs at the beginning of every tick. During this phase
  the agent provides to each reactor updates on their {\em external}
  state variables for this tick and ask them to compute their {\em
    internal} state variables values for this same tick. By doing so
  we propagate a consistent view of that state of the world throughout
  all the reactors as time advance.
